Findings

### 2019-05-13 findings.Rmd
update

![*XY plot of relative word use frequency in technical comments vs. logic comments. *](/Users/danjohnson/Dropbox/Coding_Tools/R_Environment/R_Projects/default_website/docs/initial_exploration_files/figure-html/unnamed-chunk-3-6.png)

@@

![*Log-Odds ratio comparison of words most different between Writing comments (top) and Technical comments (bottom). *](/Users/danjohnson/Dropbox/Coding_Tools/R_Environment/R_Projects/default_website/docs/initial_exploration_files/figure-html/unnamed-chunk-7-1.png)

@@

![alt text](/Users/danjohnson/Dropbox/Coding_Tools/R_Environment/R_Projects/default_website/docs/NB_2r2c_files/figure-html/unnamed-chunk-4-1.png)

![alt text](/Users/danjohnson/Dropbox/Coding_Tools/R_Environment/R_Projects/default_website/docs/NB_2r2c_files/figure-html/unnamed-chunk-6-1.png)

>>>>

![*XY plot of relative word use frequency in technical comments vs. logic comments. *](/Users/danjohnson/Dropbox/Coding_Tools/R_Environment/R_Projects/default_website/images/unnamed-chunk-3-6.png)

@@

![*Log-Odds ratio comparison of words most different between Writing comments (top) and Technical comments (bottom). *](/Users/danjohnson/Dropbox/Coding_Tools/R_Environment/R_Projects/default_website/images/unnamed-chunk-7-1.png)

@@

![](/Users/danjohnson/Dropbox/Coding_Tools/R_Environment/R_Projects/default_website/images/unnamed-chunk-4-1.png)

![](/Users/danjohnson/Dropbox/Coding_Tools/R_Environment/R_Projects/default_website/images/unnamed-chunk-6-1.png)
